\documentclass[../../main.tex]{subfiles}
\begin{document}
% Maybe consider a diffrerent strucure.
    % Start out by concluding on the general framework that has been built to enable the controller to be built. Here the FPGA must be mentioned as the interface/link. Choices which have been made on the microcontroller also. How do the two communicate?
    % Lead into the controller design. were the specifications met? Which controller design performed the best?
    % conclude what caused some issues.

%general overview
Using the ARTIX-7 FPGA and the TM4C123GH6PM microcontroller an implementation has been made to control the pan-tilt system. This implementation provides the required logic to facilitate PID-controllers to control the system.  

 

A program containing tasks for handling data transmission via SPI, communication with a user through UART, and execution of the PID-controller algorithms has been developed and implemented on the microcontroller. The tasks are scheduled by the FreeRTOS operating system.

An average CPU utilisation of \SI{46}{\percent} is determined satisfying the requirement that the PID-controllers are not to utilise more than \SI{60}{\percent} of the total CPU time. An approximate overhead of \SI{5,7}{\percent} is found and considering the CPU utilisation, it is deemed, that the overhead does not compromise the timing of the system. An UI task, utilising an UART driver handling the peripheral UART modules, has been developed to manage different user commands, for which a protocol has been designed.

Functionality has been developed to allow for communication between the microcontroller and the FPGA via the SPI protocol. 
Tests have shown messages transmitted via SPI to the FPGA, at a bit rate of \SI{13.3}{\mega\hertz}, to be received correctly 10000/10000 times. This complies with the requirement of \SI{99,9}{\percent} messages correctly received.

Functionality has been implemented on the FPGA to interface the motor encoders and keep track of the motor positions by counting the number of encoder counts relative to a reference position given by a reset routine implemented on the FPGA. Furthermore functionality to derive the velocity of the motors, based on the time between encoder counts, has been implemented.
Obtained velocity measurements have been found to be erroneous, and the effects of this are discussed in the report.   

To control the motors, functionality has been designed to produce a PWM-signal with a frequency of \SI{48.8}{\kilo\hertz}. The PWM-signal is dictated by a duty cycle reference received through SPI.

Mathematical models of the pan and tilt motors have been developed to allow for the systems to be simulated, and to be able to design PID-controllers using the pole placement method.
Single position PID-controllers have been designed for both the pan and tilt motors based on the pole placement method. Furthermore, velocity PID-controllers have been designed for the tilt motor based on the pole placement method as well as the heuristic Ziegler-Nichols method. Lastly, using each of the two velocity controllers as the inner controller in a cascaded controller design, outer position controllers have been designed based on the pole placement method. In the design phase it proved somewhat difficult to thoroughly meet all the performance specifications, while still maintaining low enough gains that the required control signals were reasonable.
The designed controllers have been implemented into the microcontroller and have been tested to evaluate the performance and compare it to the performance predicted by the model.
Here it was found that the tilt motor model seemed to be quite accurate, while the model of the pan motor is deemed inaccurate.
Contrary to expectations, it was found that the cascaded controller design did not improve performance compared to the single controller design, while at the same time being more complex to design and tune.
Tests showed that good performance of the inner controllers are crucial to a cascaded design. The Ziegler-Nichols design method gave significantly better results for designing the velocity controller compared to the model based design. This may partly be caused by an erroneous velocity feedback, the effects of which, and means to correct it, have been discussed in the report.
With an overshoot of \SI{0,8}{\percent}, a rise time of \SI{0,34}{\second} and a settling time of \SI{2,86}{\second} for the tilt motor, the single position PID-controller using the pole placement method achieved the best result.
The cascaded controller achieving the best performance, had an overshoot of \SI{14}{\percent}, a rise time of \SI{0,38}{\second} and a settling time of \SI{3,22}{\second} using the Ziegler-Nichols method. 


%tuning - resultsPI
%The Ziegler-Nichols and pole placement tuning methods are used to visualise the benefits and examine the effects on the response of the system. All simulations are made based on specifications of \SI{5}{\percent} overshoot, \SI{1,5}{\second} settling time and \SI{0,5}{\second} rise time. From the tests made in the project it is apparent that it is imperative to have knowledge of the plant to achieve a true simulation of the system. None of the tests using pole placement or Ziegler-Nichols yields a response, satisfies the requirement specifications. However it is shown that the single position controller using pole placement on the tilt motor has the best result with an overshoot of \SI{0,8}{\percent}, a settling time of \SI{2,86}{\second} and a rise time of \SI{0,34}{\second}. Being the system with most known parameters, it complies well with aforementioned statement.   %model vs. implementation

%implementation - 
%The PID-controllers are designed to control the position and velocity of the pan-tilt system and implemented using the Tustin's method. It is examined whether a single PID-controller is better than two PID-controllers in cascade. According to the tests a cascaded controller will not improve performance of the system in comparison with a single controller. The best performing cascade controller achieved an overshoot of \SI{14}{\percent}, a settling time of \SI{3,22}{\second} and a rise time of \SI{0,38}{\second}. However this does not comply with the requirement specifications. Ideally the cascaded PID-controller should improve the response of the controller, however due to imperfections in the encoders, it has not been able to achieve a satisfying response for velocity controller.  %conclusion here!

%In conclusion different methods of control theory have been examined. In spite of modelling the controllers to satisfy the requirement specifications, the implemented controllers do not comply. However it has been possible to achieve an implementation of a PID-controller, which resembles the response of simulated controllers. The cause is discussed further in the report and possible solutions are presented. Based on the tests presented in this report it seems the added velocity controller of a cascaded controller design does not yield a better overall performance, while making tuning more complex.

% FPGA - possible to control the motors (PWM), SPI,encoders, reset.
% microcontroller - Scheduling, Overhead, SPI, cpu time/utilisation.
% PID-controller - different methods. - which controllers are made?
%   - Ziegler-Nichols: results model vs. implementation
%   - Pole placement: results model vs. implementation
%   - Cascade: results? better than single controller?
%   - Did we meet the requirements in relation to overshoot, settling time and rise time?
% Other remarks

\end{document}